NoTitle

### 2017-06-12 Aplas17/sections/Formalization.tex
figures
Fixed overview. Move on to formalization.

\subsection{Syntax}

@@

\begin{figure*}[t]
\begin{mathpar}
	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	\tsuperinvk \\
	\tnew \\
	\tmethod \\
	\tintf
\end{mathpar}
\caption{Typing rules.}\label{fig:typingrules}
\end{figure*}
\bruno{Path invocation subsumes regular invocation. In other words:
e0.m(e) = e0.I::m(e) when the type of e0 is I.}
\bruno{Last time I met I told you that the typing of ``this'' is
  wrong, and this is not yet fixed. I've also told you to make all
figures at the top. In T-Method, $\Gamma$ shows up out of nowhere.
}
\bruno{Rule for new is wrong! It says that a new expression that
  creates a class with any name (even if the class does not exist) 
is valid. The paper is not even following the rules of FJ.}

@@

>>>>

\subsection{Syntax} \haoyuan{TODO: syntactic sugar; mention that path invocation subsumes
regular invocation; add explanation for interface check; use the examples to illustrate the
mbody algorithm in an intuitive way, and especially explain the two counter-examples that are
important to type soundness.}

@@

\begin{figure*}[t]
\begin{mathpar}
	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	\tsuperinvk \\
	\tnew \\
	\tmethod \\
	\tintf
\end{mathpar}
\caption{Typing rules.}\label{fig:typingrules}
\end{figure*}
\bruno{Path invocation subsumes regular invocation. In other words:
e0.m(e) = e0.I::m(e) when the type of e0 is I.}

@@

\begin{figure*}[t]
\centering
\vspace{-1ex}
\begin{tabular}{ccccc}
\includegraphics[width=2cm]{pics/p1.pdf}\hspace{4pt} &
\includegraphics[width=2cm]{pics/p2.pdf}\hspace{4pt} &
\includegraphics[width=2cm]{pics/p3.pdf}\hspace{4pt} &
\includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
\includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\
(a) & (b) & (c) & (d) & (e)
\end{tabular}
\caption{Figures..}\label{fig:pegasus}
%\saveSpaceFig
\end{figure*}

### 2017-06-12 Aplas17/sections/Overview.tex
Comments on S2
Fixed overview. Move on to formalization.

What we really expect from the language is that we keep both methods
without renaming, and the type checker does not complain about 
inheritance. But we need to find an approach to \emph{disambiguate on method
calls statically}.
\bruno{Perhaps show the solution in MIM here, and then move to problem
2 (which is being discussed next with shuffleAndDraw)}

@@

\subsection{Partial Overrides in \MIM	} \haoyuan{TODO}

\MIM{} supports two kinds of polymorphism on methods: (1) method overriding; (2) method update. A method update is similar to overriding, in the sense that it provides a refined implementation of a method. But the difference is that an update just refines one branch, since \MIM{} can preserve several conflicted branches at the same time. Whereas a method overriding will hide all its inherited original methods, in which case method conflicts are unexpectedly ignored.

For example, we define an interface \lstinline|DrawableLoggingDeck2|, where we refine the \lstinline|draw()| from \lstinline|Drawable()| by setting
the canvas invisible:
\vspace{3pt}\begin{lstlisting}
interface DrawableLoggingDeck2 extends DrawableLoggingDeck {
  void draw() updates Drawable {
    JFrame frame = new JFrame("Canvas");
    frame.setVisible(false);
    ...
  }
}
\end{lstlisting}\vspace{3pt}
Here the update specifies \lstinline|Drawable| to be refined. The use of this update ensures that both branches of \lstinline|draw()| are preserved. At the same time, we should notice that a method update is no longer considered as an original method. Some client code is shown below:
\vspace{3pt}\begin{lstlisting}
DrawableLoggingDeck2 d2 = new DrawableLoggingDeck2();
d2.Drawable::draw(); // calling draw() in DrawableLoggingDeck2
d2.Deck::draw();       // calling draw() in LoggingDeck
\end{lstlisting}\vspace{3pt}

In \MIM{}, hierarchical dispatch first finds the most specific original method (with respect to method overriding), then it finds the most specific update on that method. A counter-example is when there are two method updates on \lstinline|Drawable| in \lstinline|DrawableLoggingDeck2|, it leads to ambiguity. The compiler is supposed to forbid that during compile time.

Two rules for method updates in \MIM: updates can only refine \textbf{original} methods, and they cannot overlap method overriding. For instance, writing \lstinline|"void draw()| \lstinline|updates Deck {...}"| is disallowed in \lstinline|DrawableLoggingDeck2|, because existing two branches are \lstinline|Drawable.draw()| and \lstinline|LoggingDeck.draw()|, yet \lstinline|Deck.draw()| is already overridden. It does not really make sense to update the old branch.

>>>>

What we really expect from the language is that we keep both methods
without renaming, and the type checker does not complain about 
inheritance. But we need to find an approach to \emph{disambiguate on method
calls statically}.
\bruno{Perhaps show the solution in MIM here (i.e Section 2.4), and then move to problem
2 (which is being discussed next with shuffleAndDraw)}

@@

\subsection{Partial Overrides in \MIM	}

Method overriding is commonly supported by many OO languages as a kind of polymorphism.
We have seen that \MIM{} is able to preserve several conflicted branches simultaneously and let them coexist.
In that case, a traditional method overriding, like one in Java, will override all the inherited methods, and hence
hide all those conflicted branches. Besides, \MIM{} also allows partial overrides to offer independent extensibility.
A partial override will specify one of the branches, and only refine the method from that branch. It ensures that
other branches are not affected.

For example, we define an interface \lstinline|DrawableLoggingDeck2|, and in its definition we refine the \lstinline|draw()| from \lstinline|Drawable()| by setting
the canvas invisible:
\vspace{3pt}\begin{lstlisting}
interface DrawableLoggingDeck2 extends DrawableLoggingDeck {
  void draw() override Drawable {
    JFrame frame = new JFrame("Canvas");
    frame.setVisible(false);
    ...
  }
}
\end{lstlisting}\vspace{3pt}
Here the partial override specifies \lstinline|Drawable| to be refined. The use of it ensures that both branches of \lstinline|draw()| are preserved. At the same time, we should notice that the methods we present in previous examples are called ``original methods'', and they are actually created by ``total overrides'', rather than partial overrides. Some client code is shown below: \haoyuan{which words should we use instead of "total overrides"?}
\vspace{3pt}\begin{lstlisting}
DrawableLoggingDeck2 d2 = new DrawableLoggingDeck2();
d2.Drawable::draw(); // calling draw() in DrawableLoggingDeck2
d2.Deck::draw();       // calling draw() in LoggingDeck
\end{lstlisting}\vspace{3pt}

In \MIM{}, hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific partial override on that branch. A quick counter-example is when there are two partial overrides on \lstinline|Drawable| in \lstinline|DrawableLoggingDeck2|, it leads to ambiguity. The compiler is supposed to forbid that during compile time.

Two rules for partial overrides in \MIM: updates can only refine \textbf{original} methods, and they cannot overlap total overrides. For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableLoggingDeck2|, because existing two branches are \lstinline|Drawable.draw()| and \lstinline|LoggingDeck.draw()|, and \lstinline|Deck.draw()| is already covered. It does not really make sense to refine an old branch.
